Programming Language Foundations in Agda

### 2019-07-01 sbmf/sbmf/latex/PLFA.tex
Making a subdirectory of sbmf

%\documentclass[runningheads,oribibl]{llncs}
\documentclass[runningheads]{llncs}
\usepackage{natbib}
% \usepackage{stmaryrd}
% \usepackage{proof}
% \usepackage{amsmath}
% \usepackage{amssymb}
% \usepackage{color}
% \usepackage{bbm}
% \usepackage[greek,english]{babel}
% \usepackage{ucs}
% \usepackage[utf8x]{inputenc}
% \usepackage{autofe}
\usepackage{agda}
\usepackage{revsymb}
\usepackage{semantic}
\usepackage{graphicx}
\usepackage{url}
\renewcommand\UrlFont{\color{blue}\rmfamily}
\usepackage{stix}
\setcitestyle{round,aysep={}}

\begin{document}
\title{Programming Language Foundations in Agda}
\author{Philip Wadler}
\authorrunning{P. Wadler}
\institute{University of Edinburgh\\
  \email{wadler@inf.ed.ac.uk}}
\maketitle
%
\begin{abstract}
One of the leading textbooks for formal methods is
\emph{Software Foundations} (SF), written by Benjamin Pierce in
collaboration with others, and based on Coq. After five years using SF
in the classroom, I have come to the conclusion that Coq is not the
best vehicle for this purpose, as too much of the course needs to
focus on learning tactics for proof derivation, to the cost of
learning programming language theory.  Accordingly, I have written a
new textbook, \emph{Programming Language Foundations in Agda} (PLFA).
PLFA covers much of the same ground as SF, although it is not a
slavish imitation.

@@

Accordingly, the title of this paper, and the corresponding textbook,
\emph{Programming Language Foundations in Agda} (hence, PLFA)
also has two readings.  It may be parsed as ``(Programming Language)
Foundations in Agda'' or ``Programming (Language Foundations) in
Agda''---specifications in the proof assistant Agda both describe
programming languages and are themselves programmes.

@@

Section~3 compares Agda and Coq as vehicles for pedagogy.  Before
writing the book, it was not obvious that it was even possible;
conceivably, without tactics some of the proofs might
balloon in size. In fact, it turns out that for the results in PLFA
and SF, the proofs are of roughly comparable size, and (in my opinion)
the proofs in PLFA are more readable and have a pleasing visual
structure.

@@

\paragraph{Lambda: Introduction to lambda calculus}
Introduces lambda calculus, using a representation with named
variables and a separate typing relation. The language used is PCF
\citep{Plotkin-1977}, with variables, lambda abstraction, application,
zero, successor, case over naturals, and fixpoint. Reduction is
call-by-value and restricted to closed terms.

@@

\paragraph{DeBruijn: Inherently typed de Bruijn representation}
Introduces de Bruijn indices and the inherently-typed representation.
Emphasis is put on the structural similarity between a term and its
corresponding type derivation; in particular, de Bruijn indices
correspond to the judgment that a variable is well-typed under a given
environment.

@@

\paragraph{Inference: Bidirectional type inference}
Introduces bidirectional type inference, and applies it to convert from
a representation with named variables and a separate typing relation
to a representation de Bruijn indices with inherent types. Bidirectional
type inference is shown to be both sound and complete.

@@

PLFA and SF differ in several particulars.  PLFA begins with a computationally
complete language, PCF, while SF begins with a minimal language, simply-typed
lambda calculus with booleans.  PLFA does not include type annotations in terms,
and uses bidirectional type inference, while SF has terms with unique types and
uses type checking.  SF also covers a simple imperative language with Hoare logic,
and for lambda calculus covers subtyping, record types, mutable references, and normalisation
---none of which are treated by PLFA.  PLFA covers an inherently-typed de Bruijn
representation, bidirectional type inference, bisimulation, and an
untyped call-by-name language with full normalisation---none of which
are treated by SF.

SF has a third volume, written by Andrew Appel, on Verified Functional
Algorithms. I'm not sufficiently familiar with that volume to have a view
on whether it would be easy or hard to cover that material in Agda.
And SF recently added a fourth volume on random testing of Coq specifications
using QuickChick.  There is currently no tool equivalent to QuickChick
available for Agda.

There is more material that would be desirable to include in PLFA
which was not due to limits of time.  In future years, PLFA may be
extended to cover additional material, including mutable references,
normalisation, System F, pure type systems, and denotational
semantics.  I'd especially like to include pure type systems as they
provide the readers with a formal model close to the dependent types
used in the book.  My attempts so far to formalise pure type systems
have proved challenging, to say the least.

@@

There was also a pleasing surprise regarding the structure of the
proofs. While most proofs in both SF and PLFA are carried out by
induction over the evidence that a term is well typed, in SF the
central proof, that substitution preserves types, is carried out by
induction on terms for a technical reason
(the context is extended by a variable binding, and hence not
sufficiently ``generic'' to work well with Coq's induction tactic). In
Agda, I had no trouble formulating the same proof over evidence that
the term is well typed, and didn't even notice SF's description of the
issue until I was done.

The rest of the book was relatively easy to complete.  The closest to
an issue with proof size arose when proving that reduction is
deterministic.  There are 18 cases, one case per line.  Ten of the
cases deal with the situation where there are potentially two
different reductions; each case is trivially shown to be
impossible.  Five of the ten cases are redundant, as they just involve
switching the order of the arguments.  I had to copy the cases
suitably permuted. It would be preferable to reinvoke the proof on
switched arguments, but this would not pass Agda's termination checker
since swapping the arguments doesn't yield a recursive call on
structurally smaller arguments.  I suspect tactics could cut down the
proof significantly. I tried to compare with SF's proof that reduction
is deterministic, but failed to find that proof.

@@

PLFA puts the formal statements first, followed by informal explanation.
PLFA introduces an auxiliary relation \texttt{Progress} to capture
progress; an exercise (not shown) asks the reader to show it isomorphic
to the usual formulation with a disjunction and an existential.
Layout is used to present the auxiliary relation in inference rule form.
In Agda, any line beginning with two dashes is treated as a comment, making
it easy to use a line of dashes to separate hypotheses from conclusion
in inference rules.  The proof of proposition \texttt{progress} (the different
case making it a distinct name) is layed out carefully. The neat
indented structure emphasises the case analysis, and all right-hand
sides line-up in the same column.  My hope as an author is that students
will read the formal proof first, and use it as a tabular guide
to the informal explanation that follows.

SF puts the informal explanation first, followed by the formal proof.
The text hides the formal proof script under an icon;
the figure shows what appears when the icon is expanded.
As a teacher I was aware that
students might skip it on a first reading, and I would have to hope the
students would return to it and step through it with an interactive
tool in order to make it intelligible.  I expect the students skipped over
many such proofs.  This particular proof forms the basis for a question
of the mock exam and the past exams, so I expect most students will actually
look at this one if not all the others.

\newcommand{\ex}{\texttt{x}}
\newcommand{\why}{\texttt{y}}
\newcommand{\EL}{\texttt{L}}
\newcommand{\EM}{\texttt{M}}
\newcommand{\EN}{\texttt{N}}
\newcommand{\tee}{\texttt{t}}
\newcommand{\tick}{\texttt{\lq}}
\newcommand{\GG}{\Gamma}
\newcommand{\AY}{\texttt{A}}
\newcommand{\BE}{\texttt{B}}

(For those wanting more detail: In PLFA, variables and abstractions and
applications in the object language are written $\tick\;\ex$ and
$\lambdabar\;\ex\;{\Rightarrow}\;\EN$ and $\EL\;{\cdot}\;\EM$.  The
corresponding typing rules are referred to by ${\vdash}\tick\;()$
and ${\vdash}\lambdabar\;{\vdash}\EN$ and ${\vdash}\EL\;{\cdot}\;{\vdash}\EM$, where
${\vdash}\EL$, ${\vdash}\EM$, ${\vdash}\EN$ are the proofs that terms
$\EL$, $\EM$, $\EN$ are well typed, and `()` denotes that there cannot
be evidence that a free variable is well typed in the empty context.
It was decided to overload infix dot for readability, but not other
symbols. In Agda, as in Lisp, almost any sequence of characters is a
name, with spaces essential for separation.)

(In SF, variables and abstractions and applications in
the object language are written $\texttt{tvar}~\ex$ and
$\texttt{tabs}~\ex~\tee$ and $\texttt{tapp}~\tee_1~\tee_2$.
The corresponding typing rules are referred to as
$\texttt{T\_Var}$ and $\texttt{T\_Abs}$ and $\texttt{T\_App}$.)

@@

In Coq, interaction consists of stepping through a proof script, at
each point examining the current goal and the variables currently in
scope, and executing a new command in the script.  Tactics are a whole
sublanguage, which must be learned in addition to the language for
expressing specifications.  There are many tactics one can invoke in
the script at each point; one menu in CoqIDE lists about one hundred
tactics one might invoke, some in alphabetic submenus.  A Coq
script presents the specification proved and the tactics executed.
Interaction is recorded in a script, which the students
may step through at their leisure.  SF contains some prose descriptions
of stepping through scripts, but mainly contains scripts that students
are encouraged to step through on their own.

@@

Neat layout of definitions such as that in
Figure~\ref{fig:plfa-progress-2} in Emacs requires a monospaced font
supporting all the necessary characters.  Securing one has proved
tricky. As of this writing, we use FreeMono, but it lacks a few
characters ($\typecolon$ and $\qed$) which are loaded from fonts with a different
width.  Long arrows are necessarily more than a single character wide.
Instead, we compose reduction —→ from an em dash — and an arrow →.
Similarly for reflexive and transitive closure —↠.

@@

Such an evaluator from PLFA is shown in Figure~\ref{fig:plfa-eval},
where (inspired by cryptocurrencies) the number of steps
to execute is referred to as \emph{gas}. All of the example reduction
sequences in PLFA were computed by the evaluator and then edited to
improve readability; in addition, the text includes examples of
running the evaluator with its unedited output.

@@

(Late addition: My plea to the Agda list eventually bore fruit.  Oleg
Kiselyov directed me to unpublished remarks on his web page where he
uses the name \texttt{eval} for a proof of progress and notes ``the
very proof of type soundness can be used to evaluate sample
expressions'' \citep{Kiselyov-2009}.)

@@

\begin{figure}[p]
  \includegraphics[width=\textwidth]{figures/raw.png}
  \caption{Raw approach in PLFA}
  \label{fig:raw}
\end{figure}

\begin{figure}[t]
  \includegraphics[width=\textwidth]{figures/inherent.png}
  \caption{Inherent approach in PLFA}
  \label{fig:inherent}
\end{figure}

The second part of PLFA first discusses two different approaches to
modelling simply-typed lambda calculus.  It first presents raw
terms with named variables and a separate typing relation and
then shifts to inherently-typed terms with de Bruijn indices.
Before writing the text, I had thought the two approaches
complementary, with no clear winner.  Now I am convinced that the
inherently-typed approach is superior.

Figure~\ref{fig:raw} presents the raw approach.
It first defines $\texttt{Id}$, $\texttt{Term}$,
$\texttt{Type}$, and $\texttt{Context}$, the abstract syntax
of identifiers, raw terms, types, and contexts.
It then defines two judgements,
$\GG\:{\ni}\:\ex\:{\typecolon}\:\AY$ and
$\GG\:{\vdash}\:\EM\:{\typecolon}\:\AY$,
which hold when under context $\GG$ the variable $\ex$
and the term $\EM$ have type $\AY$, respectively.

Figure~\ref{fig:inherent} presents the inherent approach.
It first defines $\texttt{Type}$ and $\texttt{Context}$, the abstract syntax
of types and contexts, of which the first is as before and the second is
as before with identifiers dropped.  In place of the two judgements,
the types of variables and terms are indexed by a context and a type,
so that $\GG\:{\ni}\:\AY$ and $\GG\:{\vdash}\:\AY$ denote
variables and terms, respectively, that under context $\GG$ hae type $\AY$.
The indexed types closely resemble the previous judgements:
we now represent a variable or a term by the proof that it is well-typed.
In particular, the proof that a variable is well-typed in the raw approach
corresponds to a de Bruijn index in the inherent approach.

The raw approach requires more lines of code than
the inherent approach.  The separate definition of raw
terms is not needed in the inherent
approach; and one judgement in the raw approach needs to check that
$\ex \not\equiv \why$, while the corresponding judgement in the
inherent approach does not.  The difference becomes more pronounced
when including the code for substitution, reductions, and proofs of
progress and preservation.  In particular, where the raw approach
requires one first define substitution and reduction and then prove
they preserve types, the inherent approach establishes substitution at
the same time it defines substitution and reduction.

Stripping
out examples and any proofs that appear in one but not the other (but
could have appeared in both), the full development in PLFA for the raw approach takes 451
lines (216 lines of definitions and 235 lines for the proofs) and the
development for the inherent approach takes 275 lines (with
definitions and proofs interleaved).  We have 451 / 235 = 1.64,
close to the golden ratio.

The inherent approach also has more expressive power.  The raw
approach is restricted to substitution of one variable by a closed
term, while the inherent approach supports simultaneous substitution
of all variables by open terms, using a pleasing formulation due to
\citet{McBride-2005}, inspired by \citet{Goguen-and-McKinna-1997} and
\citet{Altenkirch-and-Reus-1999} and described in
\citet{Allais-et-al-2017}. In fact, I did manage to write a variant of
the raw approach with simultaneous open substitution along the lines
of McBride, but the result was too complex for use in an introductory
text, requiring 695 lines of code---more than the total for the other
two approaches combined.

The text develops both approaches because the raw approach is more
familiar, and because placing the inherent approach first would
lead to a steep learning curve.  By presenting the more long-winded
but less powerful approach first, students can see for themselves the
advantages of de Bruijn indices and inherent types.

@@

The benefits of the inherent approach 
are well known to some. The technique was introduced by
\citet{Altenkirch-and-Reus-1999}, and widely used elsewhere,
notably by \citet{Chapman-2009} and \citet{Allais-et-al-2017}.
I'm grateful to David Darais for bringing it to my attention.

@@

A special thank you to my coauthor, Wen Kokke.  For inventing ideas on
which PLFA is based, and for hand-holding, many thanks to Conor
McBride, James McKinna, Ulf Norell, and Andreas Abel.  For showing me
how much more compact it is to avoid raw terms, thanks to David
Darais.  For inspiring my work by writing SF, thanks to Benjamin
Pierce and his coauthors.  For comments on a draft of this paper, an
extra thank you to James McKinna, Ulf Norell, Andreas Abel, and
Benjamin Pierce. This research was supported by EPSRC Programme Grant
EP/K034413/1.

>>>>

%\documentclass[runningheads,oribibl]{llncs}
\documentclass[runningheads]{llncs}
\usepackage{natbib}
% \usepackage{stmaryrd}
% \usepackage{proof}
% \usepackage{amsmath}
% \usepackage{amssymb}
% \usepackage{color}
% \usepackage{bbm}
% \usepackage[greek,english]{babel}
% \usepackage{ucs}
% \usepackage[utf8x]{inputenc}
% \usepackage{autofe}
\usepackage{agda}
\usepackage{graphicx}
\usepackage{url}
\renewcommand\UrlFont{\color{blue}\rmfamily}
\usepackage{stix}
\setcitestyle{round,aysep={}}

\DeclareUnicodeCharacter{"2982}{\ensuremath{\typecolon}}  % ⦂
\DeclareUnicodeCharacter{"220E}{\ensuremath{\QED}}  % ∎

\begin{document}
\title{Programming Language Foundations in Agda}
\author{Philip Wadler}
\authorrunning{P. Wadler}
\institute{University of Edinburgh\\
  \email{wadler@inf.ed.ac.uk}}
\maketitle
%
\begin{abstract}
The leading textbook for formal methods is \emph{Software Foundations}
(SF), written by Benjamin Pierce in collaboration with others, and
based on Coq. After five years using SF in the classroom, I have come
to the conclusion that Coq is not the best vehicle for this purpose,
as too much of the course needs to focus on learning tactics for proof
derivation, to the cost of learning programming language theory.
Accordingly, I have written a new textbook, \emph{Programming Language
Foundations in Agda} (PLFA).  PLFA covers much of the same ground as
SF, although it is not a slavish imitation.

@@

Accordingly, the title of this paper, and the corresponding textbook,
\emph{Programming Language Foundations in Agda} (hence, PLFA)
also has two readings.  It may be parsed as ``(Programming Language)
Foundations in Agda'' or ``Programming (Language Foundations) in
Agda''---the specifications in the proof assistant Agda both describe
programming languages and are themselves programmes.

@@

Section~3 compares Agda and Coq as vehicles for pedagogy.  Before
writing the book, it was not obvious that it was even possible;
conceivably, without tactics some of the proofs
balloon in size. In fact, it turns out that for the results in PLFA
and SF, the proofs are of roughly comparable size, and (in my opinion)
the proofs in PLFA are more readable and have a pleasing visual
structure.

@@

\paragraph{Lambda: Introduction to lambda calculus}
Introduces lambda calculus, using a representation with named
variables and a separate typing relation. The language used is PCF,
with variables, lambda abstraction, application, zero, successor, case
over naturals, and fixpoint. Reduction is call-by-value and restricted
to closed terms.

@@

\paragraph{DeBruijn: Inherently typed de Bruijn representation}
Introduces de Bruijn numbers and the inherently-typed representation.
Emphasis is put on the structural similarity between a term and its
corresponding type derivation; in particular, de Bruijn numbers
correspond to the judgment that a variable is well-typed under a given
environment.

@@

\paragraph{Inference: Bidirectional type inference}
Introduces bidirectional type inference, and applies it to convert from
a representation with named variables and a separate typing relation
to a representation de Bruijn indices with inherent types.

@@

PLFA and SF differ in several particulars.  PLFA begins with a computationally
complete language, PCF, while SF begins with a minimal language, simply-typed
lambda calculus with booleans.  PLFA does not include type annotations in terms,
and uses bidirectional type inference, while SF has terms with unique types and
uses type checking.  SF also covers a simple imperative language with Hoare logic,
subtyping, record types, mutable references, and normalisation none of which are
treated by PLFA.  PLFA covers an inherently-typed de Bruijn
representation, bidirectional type inference, bisimulation, and an
untyped call-by-value language with full normalisation, none of which
are treated by SF.

SF has a third volume, written by Andrew Appel, on Verified Functional
Algorithms. I'm not sufficiently familiar with that volume to have a view
on whether it would be easy or hard to cover that material in Agda.

There is more material that would be desirable to include in PLFA
which was not due to limits of time.  In future years, PLFA may be
extended to cover additional material, including mutable references,
normalisation, System F, pure type systems, and denotational
semantics.  I'd especially like to include pure type systems as they
provide the readers with a formal model close to the dependent types
used in the book.  My attempts so far to formalise pure type systems
have proved challenging.

@@

There was also a pleasing surprise regarding the structure of the
proofs. While most proofs in both SF and PLFA are carried out by
induction over the evidence that a term is well typed, in SF the
central proof, that substitution preserves types, is carried out by
induction on terms, not evidence of typing, for a technical reason
(the context is extended by a variable binding, and hence not
sufficiently ``generic'' to work well with Coq's induction tactic). In
Agda, I had no trouble formulating the same proof over evidence that
the term is well typed, and didn't even notice SF's description of the
issue until I was done.

The rest of the book was relatively easy to complete.  The closest to
an issue with proof size arose when proving that reduction is
deterministic.  There are 18 cases, one case per line.  Ten of the
cases deal with the situation where there are potentially two
different reductions; each case is trivially shown to be
impossible.  Five of the ten cases are redundant, as they just involve
switching the order of the arguments.  I had to copy the cases
suitably permuted. It would be preferable to reinvoke the proof on
switched arguments, but this would not pass Agda's termination checker
since swapping the arguments doesn't yield a recursive call on
structurally smaller arguments.  (I suspect tactics could cut down the
proof significantly. I tried to compare with SF's proof that reduction
is deterministic, but failed to find that proof.)

@@

PLFA puts the formal statements first, followed by informal explanation.
PLFA introduces an auxiliary relation \texttt{Progress M} to capture
progress; an exercise (not shown) asks the reader to show it isomorphic
to the usual formulation with a disjunction and an existential.
Layout is used to present the auxiliary relation in inference rule form.
In Agda, any line beginning with two dashes is treated as a comment, making
it easy to use a line of dashes to separate hypotheses from conclusion
in inference rules.  The proof is layed out carefully, with a neat
indented structure to emphasise the case analysis, and all right-hand
sides lined-up in the same column.  My hope as an author is that students
will read the formal proof first, and use it as a tabular guide
to the informal explanation that follows.

SF puts the informal explanation first, followed by the formal proof.
The text hides the formal proof script under an icon;
the figures shows what appears when the icon is expanded.
As a teacher I was aware that
students might skip it on a first reading, and I would have to hope the
students would return to it and step through it with an interactive
tool in order to make it intelligible.  I expect the students skipped over
many such proofs.  This particular proof forms the basis for a question
of the mock exam and the past exams, so I expect most students will actually
look at this one if not all the others.

@@

In Coq, interaction consists of stepping through a proof script, at
each point examining the current goal and the variables currently in
scope, and executing a new command in the script.  Tactics are a whole
sublanguage, which must be learned in addition to the langauge for
expressing specifications.  There are many tactics one can invoke in
the script at each point; one menu in CoqIDE lists about one hundred
tactics one might invoked, some in alphabetic submenus.  A Coq
script presents the specification proved and the tactics executed.
Interaction is recorded in a script, which the students
may step through at their leisure.  SF contains some prose descriptions
of stepping through scripts, but mainly contains scripts that students
are encouraged to step through on their own.

@@

Neat layout of definitions such as that in
Figure~\ref{fig:plfa-progress-2} in Emacs requires a monospaced font
supporting all the necessary characters.  Securing one has proved
tricky. As of this writing, we use FreeMono, but it lacks a few
characters (⦂ and ∎) which are loaded from fonts with a different
width.  Long arrows are necessarily more than a single character wide.
Instead, we compose reduction —→ from an em dash — and an arrow →.
Similarly for reflexive and transitive closure —↠.

@@

Such an evaluator from PLFA is shown in Figure~\ref{fig:plfa-eval},
where (inspired by McBride and cryptocurrencies) the number of steps
to execute is referred to as \emph{gas}. All of the example reduction
sequences in PLFA were computed by the evaluator and then edited to
improve readability; in addition, the text includes examples of
running the evaluator with its unedited output.

@@

(Late addition: My plea to the Agda list eventually bore fruit.  Oleg
Kiselyov directed me to unpublished remarks on his web page where he
uses the name \texttt{eval} for a proof of progress and notes ``the
very proof of type soundness can be used to evaluate sample
expressions'' \citet{Kiselyov-2009}.)

@@

The second part of PLFA first discusses two different approaches to
modelling simply-typed lambda calculus.  It first presents ``raw''
terms with named variables and a separate typing relation and
then shifts to inherently-typed terms with de Bruijn indices.
Before writing the text, I had thought the two approaches
complementary, with no clear winner.  Now I am convinced that the
inherently-typed approach is superior.

The clearest indication comes from counting lines of code.
Stripping out examples and any proofs that appear in one but not the
other, the development for raw terms takes 451 lines (216 lines of
definitions and 235 lines for the proofs) and the development for
inherently typed terms takes 275 lines (with definitions and proofs
interleaved, as substitution cannot be defined without
also showing it preserves types).  We have 451 / 235 = 1.64, close
to the golden ratio.

Another indication is expressive power. The approach with named
variables and separate typing is restricted to substitution of one
variable by a single closed term, while de Bruijn indices with
inherent typing support simultaneous substitution of all variables by
open terms, using a pleasing formulation due to \citet{McBride-2005},
inspired by \citet{Goguen-and-McKinna-1997} and described
in \citet{Allais-et-al-2017}. In fact, I managed to extend
McBride's approach to support raw terms with named variables, but the
resulting code was too long and too complex for use in an introductory
text, requiring 695 lines of code---more than the total for the other
two approaches combined.

The text develops both approaches because named variables with
separate typing is more familiar, and placing de Bruijn indices and
inherent typing first would lead to a steep learning curve.  By
presenting the more long-winded but less powerful approach first,
students can see for themselves the advantages of de Bruijn indices
with inherent typing.

@@

The benefits of replacing raw typing by inherent are well
known to some. The technique was introduced by
\citet{Altenkirch-and-Reus-1999}, and widely used elsewhere,
notably by \citet{Chapman-2009} and \citet{Allais-et-al-2017}.
I'm grateful to David Darais for bringing it to my attention.

@@

A special thank you to my coauthor, Wen Kokke.  For inventing ideas on
which PLFA is based, and for hand-holding, many thanks to Conor
McBride, James McKinna, Ulf Norell, and Andreas Abel.  For showing me
how much more compact it is to avoid raw terms, thanks to David
Darais.  For inspiring my work by writing SF, thanks to Benjamin
Pierce and his coauthors.  For comments on a draft of this paper, an
extra thank you to James McKinna, Ulf Norell, Andreas Abel, and
Benjamin Pierce.
